Verifying Demonstrations

### 2017-11-24 paper/protocol.tex
Adapts paper to new repo structure

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}[%
    -Latex,
    item/.style={rectangle,draw},
    edge from parent/.style={}
    ]
    \tikzset{%
      %grow'=left,%
      %level distance=5em%
    }
    \node[item] (proof) {Proof share}
      child {%
        node[item] (pid) {$pid$}
        child {%
          node[item] (cid) {$cid$}
          child {%
            node[item] (manifesto) {Manifesto}
          }
        }
      }
      child {%
        node[item] (wid) {$wid$}
      }
      child {%
        node[item] (ts) {$t_s$}
      }
      child {%
        node[item] (l) {$l$}
      }
      child {%
        node[item] (wsig) {$wsig$}
      }
      ;

      \path[every node/.style={font=\small}]
      (pid) edge node [anchor=south east] {$\in$} (proof)
      (wid) edge node [anchor=east] {$\in$} (proof)
      (ts) edge node [anchor=east] {$\in$} (proof)
      (l) edge node [anchor=west] {$\in$} (proof)
      (wsig) edge node [anchor=south west] {$\in$} (proof)
      ;

      \path[every node/.style={font=\small}]
      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
      % wsig
      (l) edge[bend right] (wsig)
      (ts) edge[bend right] (wsig)
      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
        \cdot)$} (wsig)
      ;

  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }}%
  \label{fig:ProofFig}
\end{figure}%
\end{frame}

@@

Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(id)\) and 
that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]

>>>>

\begin{frame}
\begin{figure}
  \centering
  \includegraphics{proofshare.tikz}
%  \begin{tikzpicture}[%
%    -Latex,
%    item/.style={rectangle,draw},
%    edge from parent/.style={}
%    ]
%    \tikzset{%
%      %grow'=left,%
%      %level distance=5em%
%    }
%    \node[item] (proof) {Proof share}
%      child {%
%        node[item] (pid) {$pid$}
%        child {%
%          node[item] (cid) {$cid$}
%          child {%
%            node[item] (manifesto) {Manifesto}
%          }
%        }
%      }
%      child {%
%        node[item] (wid) {$wid$}
%      }
%      child {%
%        node[item] (ts) {$t_s$}
%      }
%      child {%
%        node[item] (l) {$l$}
%      }
%      child {%
%        node[item] (wsig) {$wsig$}
%      }
%      ;
%
%      \path[every node/.style={font=\small}]
%      (pid) edge node [anchor=south east] {$\in$} (proof)
%      (wid) edge node [anchor=east] {$\in$} (proof)
%      (ts) edge node [anchor=east] {$\in$} (proof)
%      (l) edge node [anchor=west] {$\in$} (proof)
%      (wsig) edge node [anchor=south west] {$\in$} (proof)
%      ;
%
%      \path[every node/.style={font=\small}]
%      (manifesto) edge node [anchor=east] {$H(\cdot)$} (cid)
%      (cid) edge node [anchor=east] {$PRF_{k_P}(\cdot)$} (pid)
%      (pid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot)$} (wid)
%      % wsig
%      (l) edge[bend right] (wsig)
%      (ts) edge[bend right] (wsig)
%      (wid) edge[bend right] node [anchor=north west] {$PRF_{k_W}(\cdot, \cdot, 
%        \cdot)$} (wsig)
%      ;
%
%  \end{tikzpicture}
  \mode<article>{%
  \caption{%
    Structure of a proof share.
    The protester \(P\)'s identifier \(pid\) is computed using the protester's 
    key \(k_P\).
    The witness \(W\)'s identifier \(wid\) is computed using the witness's key 
    \(k_W\).
    \(t_s\) is a time interval and \(l\) is the coordinates of an area.
    The protest (cause) identifier \(cid\) is the hash value of the manifesto.
  }}%
  \label{fig:ProofFig}
\end{figure}%
\end{frame}

@@

Alice must provide \iac{NIZK} proof showing that \(pid = PRF_{k_P}(cid)\) and 
that she knows a signature by the identity authority on \(k_P\).
\dots
[Details of how to do this, or maybe that will be in \cref{BuildingBlocks}. See 
issue \#27 for discussion.]
